---
title: "Acala / Karura Hubspot Dashboards"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    social: menu
    source_code: embed
---

```{css custom1, echo=FALSE}
.dataTables_scrollBody {
    max-height: 100% !important;
}
```

```{r global, include=FALSE}
library(knitr)

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)


library(kableExtra)
library(formattable)
library(lubridate)
library(flexdashboard)
library(DT)
library(subscanr)
library(ghql)
x <- GraphqlClient$new()

# Helper function to concat
`%+%` <- function(a, b) paste0(a, b)

library(reticulate)
```

```{r tokens, include=FALSE}

KSM_tokens <- getAccountBalance_acala_token("karura", window = 1, filter = 'filter: {tokenId: {in: ["KSM","LKSM"]}, total: {greaterThan: "0"}} ', endpage = 2e9)
KSM_token_wide <- dcast(KSM_tokens, accountId ~ tokenId, value.var = 'total')

DOT_tokens <- getAccountBalance_acala_token("acala", window = 1, filter = 'filter: {tokenId: {in: ["DOT","LDOT"]}, total: {greaterThan: "0"}} ', endpage = 2e9)
DOT_token_wide <- dcast(DOT_tokens, accountId ~ tokenId, value.var = 'total')

```

```{r loans, include=FALSE}

aUSD_karura <- getAccountBalance_acala_token("karura", window = 1, filter = 'filter: {tokenId: {in: ["ACA","KUSD","AUSD"]}, total: {greaterThan: "0"}} ', endpage = 2e9)
aUSD_karura_wide <- dcast(aUSD_karura, accountId ~ tokenId, value.var = 'total')


aUSD_acala <- getAccountBalance_acala_token("acala", window = 1, filter = 'filter: {tokenId: {in: ["ACA","KUSD","AUSD"]}, total: {greaterThan: "0"}} ', endpage = 2e9)
aUSD_acala_wide <- dcast(aUSD_acala, accountId ~ tokenId, value.var = 'total')


loans_acala <- getPositions_acala_loan("acala", window = 1, filter = 'filter: {collateralId: {in: ["aUSD","kUSD","ACA","DOT","LDOT","KSM","LKSM"]}} ', endpage = 2e9)
loans_acala_wide <- dcast(loans_acala, ownerId ~ collateralId, value.var = c('debitAmount','depositAmount'))


loans_karura <- getPositions_acala_loan("karura", window = 1, filter = 'filter: {collateralId: {in: ["aUSD","kUSD","ACA","DOT","LDOT","KSM","LKSM"]}} ', endpage = 2e9)
loans_karura_wide <- dcast(loans_karura, ownerId ~ collateralId, value.var = c('debitAmount','depositAmount'))

```

```{python}
from substrateinterface import SubstrateInterface
from substrateinterface.utils.ss58 import ss58_decode, ss58_encode

# Convert ss58 address from one chain to another 
# (i.e. Substrate=42, Polkadot=0, Kusama=2, Acala=10, Karura=8)
def ss58_convert(addr, fromChain, toChain):
  pk = ss58_decode(addr, valid_ss58_format = int(fromChain))
  output = ss58_encode(pk, ss58_format = int(toChain))
  return output

# ss58_convert(addr, 42, 10)
# addr = "5EChUec3ZQhUvY1g52ZbfBVkqjUY9Kcr6mcEvQMbmd38shQL"
# input_id = 42
# output_id = 10
# ss58_convert(addr, input_id, output_id)

def get_Balance(chain):
    if chain=="Polkadot":
        url = 'wss://polkadot.api.onfinality.io/public-ws'
        decimals = 10
    elif chain=="Kusama":
        url = 'wss://kusama.api.onfinality.io/public-ws'
        decimals = 12
    elif chain=="Karura":
        url = 'wss://karura.polkawallet.io'
        decimals = 12
    else:
        url = 'wss://acala-rpc-0.aca-api.network'
        decimals = 12
        
    data = []
    substrate = SubstrateInterface(url)
    for j in range(0, len(r.addrs)):
        # addr = '14QV6hfAiXyb5LBajUqWR9CrQKxfQZMkBiERpQFuoj7YBqis'
        addr = r.addrs[j]
        balance_info = substrate.get_runtime_state(
            module='System',
            storage_function='Account',
            params=[addr]).get('result')
        balance = balance_info.get('data').get('free', 0)
        outi = {"address": addr, 'BalanceNew': balance / 10**decimals}
        data.append(outi)
    return data

```


```{r balances}

karura_addr <- fread(file = '/Users/rogerbos/R_HOME/karura-reports/karura_email_balance.csv')
karura_addr <- karura_addr[!duplicated(address)]
addrs <- karura_addr$address
# n <- ceiling(nrow(karura_addr)/10)
# for (i in 0:9) {
#   print(paste0(i*n+1, ":", min(nrow(karura_addr), (i+1)*n)))
#   starti <- i*n+1
#   endi <- min(nrow(karura_addr), (i+1)*n)
#   addrs <- karura_addr$address[starti:endi]
#   kusama_balances <- py$get_Balance("Kusama")
#   kusama_balances <- rbindlist(kusama_balances)
#   fwrite(kusama_balances, "kusama_balances.csv", append = ifelse(i==0, FALSE, TRUE))
# }
kusama_balances <- fread("kusama_balances.csv")
kusama_balances[BalanceNew < 0]
karura_addr <- merge(karura_addr, kusama_balances, by = "address", all.x = TRUE)
karura_addr[, Balance := NULL]
setnames(karura_addr, "BalanceNew", "Balance")
# karura_addr[Balance != BalanceNew]


# py$ss58_convert(addr, 0, 10) # Polkadot to Acala
# py$ss58_convert(addr, 2, 8)  # Kusama to Karura

acala_addr <- fread(file = '/Users/rogerbos/R_HOME/karura-reports/acala_email_balance.csv')
acala_addr <- acala_addr[!duplicated(address)]


if (FALSE) {
  head(acala_addr)

  library(readxl)
  hack <- read_xlsx("~/Downloads/HackTrace.xlsx")
  hack <- merge(hack, acala_addr, by.x="acc", by.y="accountId", all.x = TRUE)
  hack[, c("Stolen", "acc", "email")]
  fwrite(hack, "~/Downloads/hacktrace.csv")

}









# n <- ceiling(nrow(acala_addr)/10)
# for (i in 0:9) {
#   print(paste0(i*n+1, ":", min(nrow(acala_addr), (i+1)*n)))
#   starti <- i*n+1
#   endi <- min(nrow(acala_addr), (i+1)*n)
#   addrs <- acala_addr$address[starti:endi]
#   polkadot_balances <- py$get_Balance("Polkadot")
#   polkadot_balances <- rbindlist(polkadot_balances)
#   fwrite(polkadot_balances, "polkadot_balances.csv", append = ifelse(i==0, FALSE, TRUE))
# }
polkadot_balances <- fread("polkadot_balances.csv")
polkadot_balances[BalanceNew < 0]
acala_addr <- merge(acala_addr, polkadot_balances, by = "address", all.x = TRUE)
acala_addr[, Balance := NULL]
setnames(acala_addr, "BalanceNew", "Balance")

karura_addr <- merge(karura_addr, KSM_token_wide, by = 'accountId', all.x = TRUE)
karura_addr <- merge(karura_addr, aUSD_karura_wide, by = 'accountId', all.x = TRUE)
karura_addr <- merge(karura_addr, loans_karura_wide, by.x = 'accountId', by.y = 'ownerId', all.x = TRUE)

acala_addr <- merge(acala_addr, DOT_token_wide, by = 'accountId', all.x = TRUE)
acala_addr <- merge(acala_addr, aUSD_acala_wide, by = 'accountId', all.x = TRUE)
acala_addr <- merge(acala_addr, loans_acala_wide, by.x = 'address', by.y = 'ownerId', all.x = TRUE)

```

# Karura {.tabset}

Row
----

### KSM analysis based on `r karura_addr[, .N]` users

0) None = Default
1) KSM on Kusama Only = Kusama KSM Balance > 0
2) KSM on Karura but no LKSM = Karura KSM Balance > 0
3) LKSM User = LKSM Balance > 0
4) LP User = depositAmount_LKSM > 0

```{r KSM}

# KSM
# KSM on Kusama only
# KSM on Karura but no LKSM
# LKSM user
# LP user
ksm_n <- karura_addr[, .N]
karura_addr[, KSM_Status := '0) None']
karura_addr[Balance > 0, KSM_Status := '1) KSM on Kusama Only']
karura_addr[KSM > 0, KSM_Status := '2) KSM on Karura but no LKSM']
karura_addr[LKSM > 0, KSM_Status := '3) LKSM User']
karura_addr[depositAmount_LKSM > 0, KSM_Status := '4) LP User']
ksm_tbl <- karura_addr[, .N, by = 'KSM_Status'] %>%
  setorder(KSM_Status)
ksm_tbl2 <- karura_addr[, 100*round(.N / ksm_n, 3), by = 'KSM_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(KSM_Status)
ksm_tbl <- merge(ksm_tbl, ksm_tbl2)

knitr::kable(ksm_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```

Row
----

### AUSD (on Karura) analysis based on `r karura_addr[, .N]` users

0) None = Default
1) AUSD Holder = AUSD Balance > 0
2) AUSD Vault Open = depositAmount_KSM > 0 OR depositAmount_LKSM > 0
3) Vault open but no AUSD minted = depositAmount_KSM > 0 OR depositAmount_LKSM > 0 AND (is.na(debitAmount_KSM) AND is.na(debitAmount_LKSM)

```{r KUSD}

# aUSD
# No aUSD
# aUSD holder
# aUSD vault open
# Vault open but no aUSD minted
ausd_karura_n <- karura_addr[, .N]
karura_addr[, AUSD_Status := '0) None']
karura_addr[KUSD > 0, AUSD_Status := '1) AUSD Holder']
karura_addr[depositAmount_KSM > 0 | depositAmount_LKSM > 0, AUSD_Status := '2) AUSD Vault Open']
karura_addr[depositAmount_KSM > 0 | depositAmount_LKSM > 0 & (is.na(debitAmount_KSM) & is.na(debitAmount_LKSM)), AUSD_Status := '3) Vault open but no AUSD minted']
ausd_tbl <- karura_addr[, .N, by = 'AUSD_Status'] %>%
  setorder(AUSD_Status)
ausd_tbl2 <- karura_addr[, 100*round(.N / ausd_karura_n, 3), by = 'AUSD_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(AUSD_Status)

ausd_tbl <- merge(ausd_tbl, ausd_tbl2)

knitr::kable(ausd_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```


# Acala {.tabset}

Row
----

### DOT analysis based on `r acala_addr[, .N]` users

0) None = Default
1) DOT on Polkadot Only = Polkadot DOT Balance > 0
2) DOT on Acala but no LDOT = Acala DOT Balance > 0
3) LDOT User = LDOT Balance > 0
4) LP User = depositAmount_LDOT > 0

```{r DOT}

# DOT
# DOT on Polkadot only 
# DOT on Acala but not LDOT
# LDOT users
# LP user
dot_n <- acala_addr[, .N]
acala_addr[, DOT_Status := '0) None']
acala_addr[Balance > 0, DOT_Status := '1) DOT on Polkadot Only']
acala_addr[DOT > 0, DOT_Status := '2) DOT on Acala but no LDOT']
acala_addr[LDOT > 0, DOT_Status := '3) LDOT User']
acala_addr[depositAmount_LDOT > 0, DOT_Status := '4) LP User']
dot_tbl <- acala_addr[, .N, by = 'DOT_Status'] %>%
  setorder(DOT_Status)
dot_tbl2 <- acala_addr[, 100*round(.N / dot_n, 3), by = 'DOT_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(DOT_Status)

dot_tbl <- merge(dot_tbl, dot_tbl2)

knitr::kable(dot_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```

Row
----

### AUSD (on Acala) analysis based on `r acala_addr[, .N]` users

0) None = Default
1) AUSD Holder = AUSD Balance > 0
2) AUSD Vault Open = depositAmount_KSM > 0 OR depositAmount_LKSM > 0
3) Vault open but no AUSD minted = depositAmount_KSM > 0 OR depositAmount_LKSM > 0 AND (is.na(debitAmount_KSM) AND is.na(debitAmount_LKSM)

```{r AUSD}

# aUSD
# No aUSD
# aUSD holder
# aUSD vault open
# Vault open but no aUSD minted

ausd_acala_n <- acala_addr[, .N]
acala_addr[, AUSD_Status := '0) None']
acala_addr[AUSD > 0, AUSD_Status := '1) AUSD Holder']
acala_addr[depositAmount_ACA > 0 | depositAmount_DOT > 0 | depositAmount_LDOT > 0, AUSD_Status := '2) AUSD Vault Open']
acala_addr[depositAmount_ACA > 0 | depositAmount_DOT > 0 | depositAmount_LDOT > 0 & (is.na(debitAmount_ACA) & is.na(debitAmount_DOT) & is.na(debitAmount_LDOT)), AUSD_Status := '3) Vault open but no AUSD minted']
ausd_tbl <- acala_addr[, .N, by = 'AUSD_Status'] %>%
  setorder(AUSD_Status)
ausd_tbl2 <- acala_addr[, 100*round(.N / ausd_acala_n, 3), by = 'AUSD_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(AUSD_Status)

ausd_tbl <- merge(ausd_tbl, ausd_tbl2)

knitr::kable(ausd_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```

Row
----

### ACA analysis based on `r acala_addr[, .N]` users

0) None = Default
1) ACA Staker = depositAmount_ACA > 0
2) No ACA Staking = ACA Balance > 0 
3) No ACA = is.na(ACA Balance)

```{r ACA}

# names(acala_addr)
# summary(acala_addr$debitAmount_ACA)
# summary(acala_addr$depositAmount_ACA)
# summary(loans_acala_wide$debitAmount_ACA)
# summary(loans_acala_wide$depositAmount_ACA)
# 
# tmp <- loans_acala_wide[, .(ownerId, debitAmount_ACA,depositAmount_ACA)]
# tmp <- merge(tmp, acala_addr[, .(accountId, ACA, ACA_Status)], by.x = "ownerId", by.y="accountId", all = TRUE)

                        
# ACA
# ACA staker
# No ACA staking
# No ACA
aca_n <- acala_addr[, .N]
acala_addr[, ACA_Status := '0) None']
acala_addr[depositAmount_ACA > 0, ACA_Status := '1) ACA Staker']
acala_addr[ACA > 0 && is.na(depositAmount_ACA), ACA_Status := '2) No ACA Staking']
acala_addr[is.na(ACA) | ACA == 0, ACA_Status := '3) No ACA']
aca_tbl <- acala_addr[, .N, by = 'ACA_Status'] %>%
  setorder(ACA_Status)
aca_tbl2 <- acala_addr[, 100*round(.N / aca_n, 3), by = 'ACA_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(ACA_Status)

aca_tbl <- merge(aca_tbl, aca_tbl2)

knitr::kable(aca_tbl, escape = FALSE, align = c("l",rep("r",2)) ) %>%
  kable_styling()

```

# Methodologh {.tabset}

* The Polkadot{js} *keyring.encodeAddress* function was used to convert the Acala / Karura addresses to Polkadot / Kusama addresses place in the *accountId* field.

* The Polkadot{js} *query.system.account(addr)* function was used to obtain the DOT / KSM balance for each address.

* The Subquery Network _Acala Tokens_ project was used to get balances on Acala for DOT, LDOT, ACA, and AUSD and the *Karura Tokens* project was used for Karura for KSM, LKSM, and AUSD.
  - https://explorer.subquery.network/subquery/AcalaNetwork/acala-tokens
  - https://explorer.subquery.network/subquery/AcalaNetwork/karura-tokens
  
  
* The Subquery Network *Acala Loans* project was used to get deposit and debit balances on Acala for DOT, LDOT, ACA, and AUSD and the *Karura Loans* project was used for Karura for KSM, LKSM, and AUSD.
  - https://explorer.subquery.network/subquery/AcalaNetwork/acala-loans
  - https://explorer.subquery.network/subquery/AcalaNetwork/karura-loan
  
  
* The methodology for each Token is summarized in that section.

* The Acala / Karura data is as of `r Sys.time()`. 

```{r fname}

fwrite(karura_addr, "/Users/rogerbos/karura_hubspot_20220722.csv")
fwrite(acala_addr, "/Users/rogerbos/acala_hubspot_20220722.csv")

```

