---
title: "Acala / Karura TVL Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    social: menu
    source_code: embed
params:
  network: Karura
  window: 7
  
---

```{css custom1, echo=FALSE}
.dataTables_scrollBody {
    max-height: 100% !important;
}
```

```{r global, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)

library(ggplot2)
library(kableExtra)
library(formattable)
library(lubridate)
library(flexdashboard)
library(DT)
library(subscanr)
library(formattable)
library(ghql)
x <- GraphqlClient$new()

# Helper function to concat
`%+%` <- function(a, b) paste0(a, b)

window = params$window
# window <- today() - as.Date("2021-12-31") + 1
network = params$network

# Liquidity Pool TVL ($3.72M) = totalDefiTvl = totalDexTvl + totalDexLockedTvl + homaLocked + stableCoinTvl
dex <- getDailyPools_acala_dex(network, window) %>%
  setorder(Date, pair)

dailyTVL <- dex[, .(max(updateAtBlock.id), sum(tvlUSD)), by = Date] %>%
  setnames(c("V1","V2"), c("Block","dexTVL"))

library(reticulate)
# use_python("/opt/homebrew/bin/python3.9")
```

```{python, include=FALSE}
from substrateinterface import SubstrateInterface

import pandas as pd

def getTotalIssuanceKSM():
    url = 'wss://karura.polkawallet.io'
    substrate = SubstrateInterface(url)
    hash = substrate.get_block_hash(block_id)
    timestamp = substrate.query(module='Timestamp',storage_function='Now',block_hash=hash).value
  
    # Issuance
    ksm = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': 'KSM'}], block_hash = hash)
    lksm = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': 'LKSM'}], block_hash = hash)
    result = substrate.query('AcalaOracle', 'Values', params = [{'Token': 'KSM'}], block_hash = hash)
  
    # homa = substrate.query(module='Homa',storage_function='TotalStakingBonded', block_hash = hash)
    try:
        homa = substrate.query_map(module='Homa',storage_function='StakingLedgers', block_hash = hash)
        amount = 0
        for res in homa:
            amount += res[1].value['bonded']
            
        # LKSM to KSM ratio
        ratio = lksm.value / amount 

    except:
        amount = 0
        # LKSM to KSM ratio
        ratio = 8.5
    
    # Build price DataFrame
    p = substrate.query('AcalaOracle', 'Values', params = [{'Token': 'KSM'}], block_hash = hash)
    price = p.value['value'] / 10**18
  
    bridge = (float(ksm.value / 10**12) + float(lksm.value / 10**12 / ratio)) * price
    liquidKSM = float(amount / 10**12) * price
    crowdloanTVL = (501137661910050505 / 10**12) * price
    return [bridge, liquidKSM, crowdloanTVL, block_id, ratio]

def getOraclePrices():
    if r.network=="Karura":
        url = 'wss://karura.polkawallet.io'
    else:
        url = 'wss://acala-rpc-0.aca-api.network'
      
    substrate = SubstrateInterface(url)
    hash = substrate.get_block_hash(block_id)
    timestamp = substrate.query(module='Timestamp',storage_function='Now',block_hash=hash).value
    p = substrate.query_map('AcalaOracle', 'Values', block_hash = hash)
    data = []
    for res in p:
        outi = {"token": str(res[0].value), "price": res[1].value['value'] / 10**18}
        data.append(outi)
    
    out = pd.DataFrame(data)
    return out
 
 
def getRewards():
    if r.network=="Karura":
        url = 'wss://karura.polkawallet.io'
    else:
        url = 'wss://acala-rpc-0.aca-api.network'
      
    substrate = SubstrateInterface(url)
    hash = substrate.get_block_hash(block_id)
    timestamp = substrate.query(module='Timestamp',storage_function='Now',block_hash=hash).value
  
    data = []
    rewards = substrate.query_map(module='Rewards',storage_function='PoolInfos', block_hash = hash)
    for res in rewards:
        if res[0][0] == 'Dex':
            pair = res[0].value['Dex']['DexShare']
            lp = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'DexShare': pair}], block_hash = hash)
            legs = substrate.query(module='Dex',storage_function='LiquidityPool', params = [pair], block_hash = hash)
            outi = {"pair0": str(pair[0]), "pair1": str(pair[1]), "lp": str(lp.value), "leg0": str(legs[0].value), "leg1": str(legs[1].value)}
            data.append(outi)
    
    out = pd.DataFrame(data)
    return out

def getTotalIssuanceDOT():
    url = 'wss://acala-rpc-0.aca-api.network'
    substrate = SubstrateInterface(url)
    hash = substrate.get_block_hash(block_id)
    timestamp = substrate.query(module='Timestamp',storage_function='Now',block_hash=hash).value
  
    # Total Issuance data
    dot = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': 'DOT'}], block_hash = hash)
    ldot = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': 'LDOT'}], block_hash = hash)
    lcdot = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'LiquidCrowdloan': 13}], block_hash = hash)
    
    # homa = substrate.query(module='Homa',storage_function='TotalStakingBonded', block_hash = hash)
    try:
        homa = substrate.query_map(module='Homa',storage_function='StakingLedgers', block_hash = hash)
        amount = 0
        for res in homa:
            amount += res[1].value['bonded']
            
        # LKSM to KSM ratio
        ratio = ldot.value / amount 

    except:
        amount = 0
        # LDOT to DOT ratio
        ratio = 10
    
    # Build price DataFrame
    tmp = []
    p = substrate.query_map('AcalaOracle', 'Values', block_hash = hash)
    outi = {"id": {'Token': 'AUSD'}, "price": 1}
    tmp.append(outi)
    for res in p:
      outi = {"id": res[0].value, "price": res[1].value['value'] / 10**18}
      tmp.append(outi)
      if res[0].value=={'Token': 'DOT'}:
        outi = {"id": {'LiquidCrowdloan': 13}, "price": res[1].value['value'] / 10**18 / 1.4}
        tmp.append(outi)
        outi = {"id": {'Token': 'LDOT'}, "price": res[1].value['value'] / 10**18 / ratio}
        tmp.append(outi)
  
    # Price lookup function
    p = substrate.query('AcalaOracle', 'Values', params = [{'Token': 'DOT'}], block_hash = hash)
    price = p.value['value'] / 10**18
    
    # Decimals lookup function
    tmp = [{'id': {'Token': 'ACA'}, 'decimals': 12}, {'id': {'Token': 'DOT'}, 'decimals': 10}, {'id': {'Token': 'LDOT'}, 'decimals': 10}, {'id': {'LiquidCrowdloan': 13}, 'decimals': 10}, {'id': {'Token': 'AUSD'}, 'decimals': 12}]
    decimals = pd.DataFrame(tmp)
    def getDecimals(token):
      return int(decimals[decimals['id'] == token]['decimals'])        
  
    bridge = (float(dot.value / 10**10) + float(ldot.value / 10**10 / ratio)) * price
    liquidDOT = float(amount / 10**10) * price
    lcDOT = float(lcdot.value / 10**10) * price
    crowdloanTVL = (325159802323576263 / 10**10) * price
    return [bridge, liquidDOT, crowdloanTVL, lcDOT, block_id, ratio]

```



```{r tvl, cache = TRUE, include=FALSE}

# dailyTVL[, M := month(Date) %+% year(Date)]
# dailyTVL[, maxDate := max(Date), by = M]
# dailyTVL <- dailyTVL[Date == maxDate]

# LP Token Staking TVL = totalDexTvl = useTotalDexPoolTVL()
# totalDexLockedTvl = useTotalStaking() = api.query.dex?.liquidityPool
# KSM Bridge TVL = totalIssuanceKSM = useTotalIssuance('KSM') = api.query.tokens?.totalIssuance
dailyTVL[, bridgeTVL := 0]
# Liquid KSM TVL = totalLocked in Homa = useState()
dailyTVL[, liquidStakingTVL := 0]
# homeLocked = totalStaking * price
dailyTVL[, crowdloanTVL := 0]
dailyTVL[, LPTokenStakingTVL := 0]
if (tolower(network) == "acala") dailyTVL[, lcdotTVL := 0]

for (i in 1:nrow(dailyTVL)) {
  py_run_string("block_id = " %+% dailyTVL$Block[i])
  if (tolower(network) == "karura") {
    tmp = py$getTotalIssuanceKSM()
  } else {
    tmp = py$getTotalIssuanceDOT()
    dailyTVL$lcdotTVL[i] <- tmp[4]
  }
  dailyTVL$bridgeTVL[i] <- tmp[1]
  dailyTVL$liquidStakingTVL[i] <- tmp[2]
  dailyTVL$crowdloanTVL[i] <- tmp[3]
  
  # LPTokenStakingTVL 
  rewards1 <- py$getRewards()
  rewards <- as.data.table(rewards1)
  # sort(unique(c(rewards$pair0, rewards$pair1)))
  rewards[, pair0 := fixToken(pair0)]
  rewards[, pair1 := fixToken(pair1)]
  rewards <- merge(rewards, tokens, by.x = 'pair0', by.y="Token")
  setnames(rewards, "decimals", "decimals0")
  rewards[, Name := NULL]
  rewards <- merge(rewards, tokens, by.x = 'pair1', by.y="Token")
  setnames(rewards, "decimals", "decimals1")
  rewards[, Name := NULL]
  rewards[, decimals0 := as.numeric(decimals0)]
  rewards[, decimals1 := as.numeric(decimals1)]
  rewards[, lpDecimals := 12]
  rewards[pair0=='DOT' & pair1=='LCDOT', lpDecimals := 10]
  rewards[, lp := as.numeric(lp) / 10**lpDecimals]
  rewards[, leg0 := as.numeric(leg0) / 10**decimals0]
  rewards[, leg1 := as.numeric(leg1) / 10**decimals1]
  
  price = py$getOraclePrices() %>%
    as.data.table
  price[, token := fixToken(token)]
  
  rewards <- merge(rewards, price, by.x = "pair0", by.y="token", all.x = TRUE)
  setnames(rewards, "price", "price0")
  rewards <- merge(rewards, price, by.x = "pair1", by.y="token", all.x = TRUE)
  setnames(rewards, "price", "price1")
  rewards[pair0 %in% c('KUSD', "AUSD"), price0 := 1]
  rewards[pair1 %in% c('KUSD', "AUSD"), price1 := 1]
  rewards[, tvl := leg0 * price0 + leg1 * price1]
  rewards[is.na(tvl), tvl := (leg0 * price0) * 2]
  rewards[is.na(tvl), tvl := (leg1 * price1) * 2]
  rewards[, lpPrice := tvl / lp]  
  dailyTVL$LPTokenStakingTVL[i] <- sum(rewards$tvl, na.rm = TRUE)

}



# stableCoinTvl
# const stableCoinTVL = useTotalLocked(); = api.query.loans?.totalPositions
collateral <- getLoansDailyCollateral_acala_loan(network, window, staging = FALSE) %>%
  setorder(Date, collateral.id)
stableCoinTvl <- collateral[, sum(depositVolumeUSD), by = Date] %>%
  setnames("V1", "stableCoinTVL")
dailyTVL <- merge(dailyTVL, stableCoinTvl, by = "Date", all.x = TRUE)

# If monthly, remove these fields
try(dailyTVL[, M := NULL])
try(dailyTVL[, maxDate := NULL])

# Make columns numeric
for (col in names(dailyTVL)[-1]) set(dailyTVL, j=col, value=as.numeric(dailyTVL[[col]])) 
if (tolower(network) == "acala") {
  dailyTVL[, OverallTVL := dexTVL + LPTokenStakingTVL + bridgeTVL + liquidStakingTVL + lcdotTVL + stableCoinTVL]
} else {
  dailyTVL[, OverallTVL := dexTVL + LPTokenStakingTVL + bridgeTVL + liquidStakingTVL + stableCoinTVL]
}

# merge history
history <- fread(network %+% "_TVL.csv")
history[, Date := as.Date(Date)]
mindate <- min(dailyTVL$Date)
dailyTVL <- rbind(history[Date < mindate], dailyTVL, use.names = TRUE)
fwrite(dailyTVL, file = network %+% "_TVL.csv")


```

# `r network` {.tabset}

Row
----

### Components of Total Value Locked

```{r k_plot1}

if (tolower(network) == "acala") {
  dat <- melt(data = dailyTVL[, .(Date, dexTVL, LPTokenStakingTVL, bridgeTVL, liquidStakingTVL, lcdotTVL, stableCoinTVL)], 
            id.vars = "Date",
            value.name = "TVL")
  cols <- c('dexTVL', 'LPTokenStakingTVL', 'bridgeTVL', 'liquidStakingTVL', 'LCDOTTVL', 'stableCoinTVL')
} else {
  dat <- melt(data = dailyTVL[, .(Date, dexTVL, LPTokenStakingTVL, bridgeTVL, liquidStakingTVL, stableCoinTVL)], 
            id.vars = "Date",
            value.name = "TVL")
  cols <- c('dexTVL', 'LPTokenStakingTVL', 'bridgeTVL', 'liquidStakingTVL', 'stableCoinTVL')
  
}
dat[, TVL := TVL / 1e6]
 
# Stacked
ggplot(dat, aes(fill=variable, y=TVL, x=Date)) + 
    geom_bar(position="stack", stat="identity") +
    ggtitle(label="Components of Total Value Locked") + 
    ylab("Totval Value Locked (in millions USD)")

```

Row
----

### Overall Total Value Locked (TVL)

* *The Overall TVL in the table below does not includes the Crowdloan TVL, which also seems to be the case on the http://stats.`r tolower(network)`.network site.*

```{r k_tvl}

knitr::kable(dailyTVL, escape = FALSE, format.args = list(big.mark = ",")) %>%
  kable_styling()

```

Row
----

### Sources and Notes

Please click on the *Source Code* link at the top of the document to see the full source code.  Here is a summary:

#### dexTVL 

- sum of tvlUSD from the xx function in the [subscanr](https://github.com/rogerjbos/subscanr) package for R.  You can also use the [Karura-dex](https://explorer.subquery.network/subquery/AcalaNetwork/karura-dex) project hosted on Subquery Network with this query:
```
{ 
  dailyPools { 
    nodes { 
      timestamp token0 {id} token1 {id} feeRateUSD dailyTradeVolumeUSD totalTVL txCount updateAtBlock {id}  
    } 
  } 
}
```

#### LPTokenStakingTVL
- ACA (or KAR) obtained from the [py-substrate-interface](https://github.com/polkascan/py-substrate-interface) using function *substrate.query(module='Rewards',storage_function='PoolInfos', block_hash = hash)*
- mulitplied by ACA (or KAR) price for the specific block number

#### BridgeTVL
- KSM (or DOT) obtained from the [py-substrate-interface](https://github.com/polkascan/py-substrate-interface) using function *substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': 'KSM'}], block_hash = hash)*
- LKSM (or LDOT) obtained from function *substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': 'LKSM'}], block_hash = hash)*
- both mulitplied by KSM (or DOT) price for the specific block number

#### liquidStakingTVL
- KSM (or DOT) obtained from the [py-substrate-interface](https://github.com/polkascan/py-substrate-interface) using function *substrate.query(module='Homa',storage_function='TotalStakingBonded', block_hash = hash)*
- mulitplied by KSM (or DOT) price for the specific block number

#### lcdotTVL (Acala only)
- LCDOT obtained from the [py-substrate-interface](https://github.com/polkascan/py-substrate-interface) using function *substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'LiquidCrowdloan': 13}], block_hash = hash)*
- mulitplied by DOT price for the specific block number

#### stableCoinTVL
- sum of depositVolumeUSD from the *getLoansDailyCollateral_acala_loan* function in the [subscanr](https://github.com/rogerjbos/subscanr) package for R.  You can also use the [Karura-loan]https://explorer.subquery.network/subquery/AcalaNetwork/karura-loan) project hosted on Subquery Network with this query:
```
{ 
  dailyCollaterals { 
    nodes { 
      collateral {id} depositAmount debitAmount depositVolumeUSD debitVolumeUSD
      depositChangedUSD debitChangedUSD debitExchangeRate timestamp txCount 
    } 
  } 
}
```
