---
title: "Acala / Karura Liquidations"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    social: menu
    source_code: embed
params:
  network: Karura
---

```{css custom1, echo=FALSE}
.dataTables_scrollBody {
    max-height: 100% !important;
}
```

```{r global, cache = FALSE, include=FALSE}

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)

library(dygraphs)
library(kableExtra)
library(formattable)
library(lubridate)
library(flexdashboard)
library(DT)
library(subscanr)
library(ghql)
x <- GraphqlClient$new()
# source("~/R_HOME/subscanr/R/subql_query.R")

network <- params$network

library(reticulate)
# use_python("/opt/homebrew/bin/python3.9")

```


```{r swaps, cache = FALSE, include=FALSE}

swaps2 <- getDailyPools_acala_dex(network, 1)
tvl <- swaps2[date == max(date)]
stable_dex_pool_size <- tvl[grep("USD", tvl$pair), sum(abs(tvlUSD))]

if (tolower(network) == "acala") {
  unsafe <- getLiquidateUnsafeCDP_acala_loan(network, 90, staging = TRUE)
  swaps <- fread("~/data/subscan/Acala_dex_Swap.csv")
} else {
  unsafe <- getLiquidateUnsafeCDP_acala_loan(network, 90, staging = TRUE)
  swaps <- fread("~/data/subscan/Karura_dex_Swap.csv")
}
swaps <- unique(swaps, by = "event_index")
summary(swaps$time)
swaps[, token0 := fixToken(token0)]
swaps[, token1 := fixToken(token1)]
swaps[, token2 := fixToken(token2)]
swaps[, token3 := fixToken(token3)]
swaps <- merge(swaps, tokens, by.x="token0", by.y="Token", all.x = TRUE) %>% 
  setnames("decimals", "decimals0")
swaps[, Name := NULL]
swaps <- merge(swaps, tokens, by.x="token1", by.y="Token", all.x = TRUE) %>% 
  setnames("decimals", "decimals1")
swaps[, Name := NULL]
swaps <- merge(swaps, tokens, by.x="token2", by.y="Token", all.x = TRUE) %>% 
  setnames("decimals", "decimals2")
swaps[, Name := NULL]
swaps <- merge(swaps, tokens, by.x="token3", by.y="Token", all.x = TRUE) %>% 
  setnames("decimals", "decimals3")
swaps[, Name := NULL]

# swaps[amount0 > 0 & is.na(divisor0)]
swaps[amount0 > 0 & is.na(decimals0), decimals0 := 12]
swaps[amount1 > 0 & is.na(decimals1), decimals1 := 12]
swaps[amount2 > 0 & is.na(decimals2), decimals2 := 12]
swaps[amount3 > 0 & is.na(decimals3), decimals3 := 12]

swaps[, float0 := as.numeric(amount0) / 10**as.numeric(decimals0)]
swaps[, float1 := as.numeric(amount1) / 10**as.numeric(decimals1)]
swaps[, float2 := as.numeric(amount2) / 10**as.numeric(decimals2)]
swaps[, float3 := as.numeric(amount3) / 10**as.numeric(decimals3)]

ce <- function(a, b) ifelse(abs(as.numeric(a) - as.numeric(b)) < 5, TRUE, FALSE)

getTarget <- function(block, collateral, id) {
  # i=486; block = cdp[i, block_num]; id = cdp[i, CurrencyId]; collateral = cdp[i, BadDebtPenalty]
  # cdp[i]
  # id = "LCDOT"; collateral=24860766062516
  # tprice <- swaps[(token0 == id | token1 == id | token2 == id | token3 == id),
  #                .(block_num, time, token0, token1, token2, token3, amount0, amount1, amount2, amount3, float0, float1, float2, float3)]

  
  tprice <- swaps[block_num == block & (token0 == id | token1 == id | token2 == id | token3 == id),
                 .(block_num, time, token0, token1, token2, token3, amount0, amount1, amount2, amount3, float0, float1, float2, float3)]

  # check for exact match using collateral amount
  tprice_exact <- tprice[(ce(amount0, collateral) | ce(amount1, collateral) | ce(amount2, collateral) | ce(amount3, collateral))]
  if (nrow(tprice_exact) == 1) {
    tprice <- tprice_exact
    tprice[, n := "exact"]
  } else if (nrow(tprice_exact) == 0) {
    tprice[, n := .N]
  }

  tprice[, trade := 0]
  tprice[token0 == id, trade := amount0]
  tprice[token1 == id, trade := amount1]
  tprice[token2 == id, trade := amount2]
  tprice[token3 == id, trade := amount3]
  tprice[, stable := 0]
  tprice[token0 %in% c("AUSD","KUSD"), stable := amount0]
  tprice[token1 %in% c("AUSD","KUSD"), stable := amount1]
  tprice[token2 %in% c("AUSD","KUSD"), stable := amount2]
  tprice[token3 %in% c("AUSD","KUSD"), stable := amount3]
  tprice[stable > 0, tradePrice := stable /  trade]
  
  tradeprice <- tprice$tradePrice
  n <- tprice$n
  # fix subscan price for DOT & LCDOT (they are using wronge decimal places)
  if (id %in% c("DOT","LCDOT")) tradeprice <- tradeprice / 100
  tradeprice[1]
  
}


getTarget_n <- function(block, collateral, id) {
  # i=485; block = cdp[i, block_num]; id = cdp[i, CurrencyId]; collateral = cdp[i, BadDebtPenalty]
  # cdp[i]
  
  tprice <- swaps[block_num == block & (token0 == id | token1 == id | token2 == id | token3 == id),
                 .(block_num, time, token0, token1, token2, token3, amount0, amount1, amount2, amount3, float0, float1, float2, float3)]

  # check for exact match using collateral amount
  tprice_exact <- tprice[(ce(amount0, collateral) | ce(amount1, collateral) | ce(amount2, collateral) | ce(amount3, collateral))]
  if (nrow(tprice_exact) == 1) {
    tprice <- tprice_exact
    tprice[, n := "exact"]
  } else if (nrow(tprice_exact) == 0) {
    tprice[, n := .N]
  }
  tprice$n[1]

}

getOracle <- function(myblock, id) {
  # i=1; myblock = cdp[i, block_num]; id = cdp[i, CurrencyId]
  # i=1; myblock = 688263; id ="LKSM"
  
  if (id == "LKSM") {
    ratio0 <- swaps[block_num <= myblock & (pair0 == "KSM:LKSM" | pair1 == "KSM:LKSM" | pair2 == "KSM:LKSM"),  
                 .(block_num, token0, token1, token2, token3, amount0, amount1, amount2, amount3, float0, float1, float2, float3)]
    ratio0[token0 == "LKSM" & token1 == "KSM", ratio := float1 / float0]
    ratio0[token1 == "LKSM" & token0 == "KSM", ratio := float0 / float1]
    
    ratio0[token1 == "LKSM" & token2 == "KSM", ratio := float2 / float1]
    ratio0[token2 == "LKSM" & token1 == "KSM", ratio := float1 / float2]
    
    ratio0[token2 == "LKSM" & token3 == "KSM", ratio := float3 / float2]
    ratio0[token3 == "LKSM" & token2 == "KSM", ratio := float2 / float3]
    setorder(ratio0, -block_num)
    ratio <- ratio0[1:10, median(ratio)]
    # default if no dex ratio available
    if (is.na(ratio)) ratio <- .1
    oracle <- price[block == myblock & mytoken == "KSM", oracle] * ratio
    
  } else if (id == "LCDOT") {
    ratio0 <- swaps[block_num <= myblock & (pair0 == "DOT:LCDOT" | pair1 == "DOT:LCDOT" | pair2 == "DOT:LCDOT"),  
                 .(block_num, token0, token1, token2, token3, amount0, amount1, amount2, amount3, float0, float1, float2, float3)]
    ratio0[token0 == "LCDOT" & token1 == "DOT", ratio := float1 / float0]
    ratio0[token1 == "LCDOT" & token0 == "DOT", ratio := float0 / float1]
    
    ratio0[token1 == "LCDOT" & token2 == "DOT", ratio := float2 / float1]
    ratio0[token2 == "LCDOT" & token1 == "DOT", ratio := float1 / float2]
    
    ratio0[token2 == "LCDOT" & token3 == "DOT", ratio := float3 / float2]
    ratio0[token3 == "LCDOT" & token2 == "DOT", ratio := float2 / float3]
    setorder(ratio0, -block_num)
    ratio <- ratio0[1:10, median(ratio)]
    oracle <- price[block == myblock & mytoken == "DOT", oracle] * ratio
    
  } else {
    oracle <- price[block == myblock & mytoken == id, oracle]
  }
  oracle
  
}

am <- get_subscan_events(nobs = 5000, network = network, module = 'auctionmanager', call = '', start_page = 1, extract = TRUE)
dealt <- am$auctionmanager_CollateralAuctionDealt[, .(block_num, CurrencyId, CollateralAmount, WinnerId, PaymentAmount)]
dealt[, CollateralAmount := as.numeric(CollateralAmount)]
dealt[, PaymentAmount := as.numeric(PaymentAmount)]
dealt[, CurrencyId := fixToken(CurrencyId)]
dealt[, WinnerId := as.character(WinnerId)]

dextake <- am$auctionmanager_DEXTakeCollateralAuction[, 
          .(event_id, time, block_num, CurrencyId, SupplyCollateralAmount, TargetStableAmount)]
dextake[, SupplyCollateralAmount := as.numeric(SupplyCollateralAmount)]
# Add TradePrice and AvgDexPrice
dextake[, CurrencyId := fixToken(CurrencyId)]
dextake[, SupplyCollateralAmount := as.numeric(SupplyCollateralAmount)]
dextake[, TargetStableAmount := as.numeric(TargetStableAmount)]

cdp_rawdata <- get_subscan_events(nobs = 5000, network = network, module = 'cdpengine', call = 'LiquidateUnsafeCDP', start_page = 1, extract = TRUE)
cdp <- cdp_rawdata$cdpengine_LiquidateUnsafeCDP[, .(event_id, time, block_num, CurrencyId, CollateralAmount, BadDebtValue)]
cdp[, CurrencyId := fixToken(CurrencyId)]
cdp[, CollateralAmount := as.numeric(CollateralAmount)]
cdp[, BadDebtValue := as.numeric(BadDebtValue)]
cdp[, BadDebtPenalty := as.numeric(BadDebtValue) * 1.15]
cdp[block_num < 964126 & CurrencyId %in% c("KSM","LKSM"), BadDebtPenalty := as.numeric(BadDebtValue) * 1.12]
cdp[block_num < 486181 & CurrencyId =="KSM", BadDebtPenalty := as.numeric(BadDebtValue) * 1.17]

# Needed oracle prices
price <- rbind(cdp[, .(block_num, CurrencyId)], 
               dextake[, .(block_num, CurrencyId)], 
               dealt[, .(block_num, CurrencyId)])
price[, CurrencyId := gsub("LDOT", "DOT", CurrencyId)]
price[, CurrencyId := gsub("LCDOT", "DOT", CurrencyId)]
price[, CurrencyId := gsub("LKSM", "KSM", CurrencyId)]
price <- unique(price)
setnames(price, c("block_num","CurrencyId"), c("block","token"))
price[, chain := network]  
price[, oracle := "0"]

```


```{python}

from substrateinterface import SubstrateInterface
# substrate.rpc_request("system_properties", []).get('result')

from datetime import datetime
import pandas as pd
import numpy as np
from datetime import date

data = []
if (r.network == "Acala"):
  url = 'wss://acala-rpc-0.aca-api.network'
else:
  url = 'wss://karura.polkawallet.io'
substrate = SubstrateInterface(url)
for j in range(0, len(r.price)):
  try:
    block = int(r.price.loc[j, 'block'])
    token = r.price.loc[j, 'mytoken']
    hash = substrate.get_block_hash(block_id = block)        
    result = substrate.query('AcalaOracle', 'Values', params = [{'Token': token}], block_hash = hash)
    price = result.value['value'] / 10**18
    outi = {"token": token, "block": block, 'price': price}
    del price
    del result
  except Exception as e:
    outi = {"token": token, "block": block, 'price': -1}
  data.append(outi)
price_api = pd.DataFrame(data)

```






```{r price, cache = FALSE, include=FALSE}

# Get trade prices
price <- py$price_api %>%
  as.data.table %>%
  setnames(c("mytoken", "block", "oracle"))

cdp[, n := getTarget_n(block_num, BadDebtPenalty, CurrencyId), 
      by = .(block_num, BadDebtPenalty, CurrencyId)]
cdp[, TradePrice := getTarget(block_num, BadDebtPenalty, CurrencyId), 
      by = .(block_num, BadDebtPenalty, CurrencyId)]
cdp[, OraclePrice := getOracle(block_num, CurrencyId),
      by = .(block_num, CurrencyId)]
cdp[, Slippage := (1 - (TradePrice / OraclePrice)) * 100]

dextake[, TradePrice := getTarget(block_num, SupplyCollateralAmount, CurrencyId), 
      by = .(block_num, SupplyCollateralAmount, CurrencyId)]
dextake[, OraclePrice := getOracle(block_num, CurrencyId),
      by = .(block_num, CurrencyId)]
dextake[, Slippage := (1 - (TradePrice / OraclePrice)) * 100]

```


```{r false, cache = FALSE, include=FALSE}

if (FALSE) {
  # i=3; block = cdp[i, block_num]; id = cdp[i, CurrencyId]; collateral = cdp[i, BadDebtPenalty]
  
  cdp[, -"event_id"]
  cdp[n==1, .N] / cdp[, .N]
  cdp[is.na(TradePrice), .N] / cdp[, .N]

  
  cdp[block_num=='996280']

  cdp[is.na(TradePrice)]
  swaps[block_num == 996280]
        
    

  # cdp[, .N, by = "CurrencyId"]
  # 
  # ####################################################
  # # write json file for prices
  # price <- rbind(cdp[, .(block_num, CurrencyId)], 
  #                dextake[, .(block_num, CurrencyId)], 
  #                dealt[, .(block_num, CurrencyId)])
  # price[, CurrencyId := gsub("LDOT", "DOT", CurrencyId)]
  # price[, CurrencyId := gsub("LCDOT", "DOT", CurrencyId)]
  # price[, CurrencyId := gsub("LKSM", "KSM", CurrencyId)]
  # price <- unique(price)
  # setnames(price, c("block_num","CurrencyId"), c("block","mytoken"))
  # price[, chain := network]  
  # price[, oracle := "0"]
  # write(toJSON(price[, .(chain, block, mytoken, oracle)]), 
  #       file = "/Users/rogerbos/subquery/price/" %+% network %+% ".json")
  # 
  
}

```


# Bots {.tabset}

Rows
---

### `r network` Liquidation Bots (auctionmanager : CollateralAuctionDealt)

* `r network` has a stable dex pool size of __$`r format(stable_dex_pool_size, big.mark=",")`__.  

* There were __`r length(unique(dealt$WinnerId))`__ unique liquidation bots that participated in __`r nrow(dealt)`__ auctions, with the following distribution:

```{r}

kable(dealt[, .N, by = WinnerId], align='rr') %>%
  kable_styling(c("striped", "condensed"), full_width = FALSE)

```

Rows
---

### `r network` CollateralAuctionDealt raw data

```{r}

mutate_if(dealt, is.numeric, function(x) {cell_spec(x=round(x,2))}) %>%
kable(escape = FALSE, align = "r") %>%
kable_styling(c("striped", "condensed"), full_width = FALSE)

```


# DEX {.tabset}

Rows
---

### `r network` DEX Take Action (auctionmanager : DEXTakeCollateralAuction)

* The DEX handles the liquidations in cases where there are no bot auctions.  There were __`r nrow(dextake)`__ auctions that were completed by the DEX (instead of bots) between __`r dextake[, min(time)]`__ and __`r dextake[, max(time)]`__.  There were __`r dextake[is.na(TradePrice), .N]`__ missing trade prices.  

* The equal-weighted average slippage was __`r round(mean(dextake[Slippage > 0, Slippage]),2)`%__.

* The volume-weighted average slippage was __`r round(weighted.mean(dextake[Slippage > 0, Slippage], dextake[Slippage > 0, TargetStableAmount]),2)`%__.

* The max slippage was __`r round(max(dextake[Slippage > 0, Slippage]),2)`%__ which occured on __`r dextake[Slippage == max(dextake[Slippage > 0, Slippage]), time]`__.

* There were __`r dextake[Slippage < 0, .N]`__ observations with negative slippage that were excluded from the above calculations.

Rows
---

```{r plot1}

dygraph(dextake[, .N, by = as.Date(time)], main = network %+% " DEX Liquidations") %>% 
        dyStackedBarChart()

```


Rows
---

```{r plot2}

dygraph(dextake[, mean(Slippage), by = as.Date(time)], main = network %+% " DEX Average Slippage") %>% 
        dyStackedBarChart()

```

Rows
---

### `r network` DEXTakeActionAuction raw data

The following data is from the DEX auctions.  The SupplyCollateralAmount is how much debt was sold in the auction and the TargetStableAmount is how much was received, resulting in the following Trade Price:

$$ TradePrice = \frac{TargetStableAmount}{SupplyCollateralAmount} $$
The market price (OraclePrice) was supplied by the `acalaOracle` function based on the onchain data for the specific block and the slippage is calculated as follows:

$$ Slippage = 1 - \frac{TradePrice}{OraclePrice} $$
---

```{r}

mutate_if(dextake, is.numeric, function(x) {cell_spec(x=round(x,2))}) %>%
  kable(escape = FALSE, align = "r") %>%
  kable_styling(c("striped", "condensed"), full_width = FALSE)

```


# CDP {.tabset}

Rows
---

### `r network` CDP Liquidate Unsafe (cdpengine : LiquidateUnsafeCDP)

* The CDP handles the liquidations via exchanges.  There were __`r nrow(cdp)`__ exchanges that were completed by the CDP engine between __`r cdp[, min(time)]`__ and __`r cdp[, max(time)]`__, but the statistics below are based on __`r cdp[!is.na(TradePrice), .N]`__ observations with an identifiable swap trade price.  

* The equal-weighted average slippage was __`r round(mean(cdp[Slippage > 0, Slippage]),2)`%__.

* The volume-weighted average slippage was __`r round(weighted.mean(cdp[Slippage > 0, Slippage], cdp[Slippage > 0, BadDebtValue]),2)`%__.

* The max slippage was __`r round(max(cdp[Slippage > 0, Slippage]),2)`%__ which occured on __`r cdp[Slippage == max(cdp[Slippage > 0, Slippage]), time]`__.

* There were __`r cdp[Slippage < 0, .N]`__ observations with negative slippage that were excluded from the above calculations.

Rows
---

```{r plot3}

dygraph(cdp[, .N, by = as.Date(time)], main = network %+% " CDP Liquidations") %>% 
        dyStackedBarChart()

```


Rows
---

```{r plot4}

dygraph(cdp[, mean(Slippage), by = as.Date(time)], main = network %+% " CDP Average Slippage") %>% 
        dyStackedBarChart()

```



Rows
---

### `r network` CDPLiquidateUnsafe raw data

The following data is from the CDP liquidations.  For the DEX auction we are able to calculate the trade price from the given SupplyCollateralAmount and TargetStableAmount, which are provided on chain.   For the CDP liquidations we have to lookup the trade price based on the swaps.  We do this by matching 1) the block number, 2) collateral id, and 3) the swap amount with the bad debt amount multiplied by the 15% penalty (BadDebtPenalty).

This worked perfectly for __`r round(cdp[n=="exact", .N] / cdp[, .N], 3) * 100`%__ of the observations, but there were __`r cdp[is.na(TradePrice), .N]`__ liquidations where the corresponding swap transaction could not be located:


```{r}

mutate_if(cdp[is.na(TradePrice)], is.numeric, function(x) {cell_spec(x=round(x,2))}) %>%
  kable(escape = FALSE, align = "r") %>%
  kable_styling(c("striped", "condensed"), full_width = FALSE)

```


The above transactions do not show up on [Subscan](https://acala.subscan.io/block) or on [Subquery](https://explorer.subquery.network/subquery/AcalaNetwork/acala-dex).  For Subquery you would have to use the following query and paste in the relevant block number: 

```
query {
  swaps (filter: {blockId: {equalTo: "1749958"}}) {
    nodes {
      id address {id} pool {id}  token0 {id} token1 {id} token0InAmount token1OutAmount tradePath price0 price1
      block {id} extrinsic {id} timestamp        }
  }
}
```

In addition, there were `r cdp[n != "exact" & !is.na(TradePrice), .N]` observations were there was a DEX transaction in the specified block, but the BadDebtPenalty amount did not match the transaction amount.  Therefore there is no way to know for sure that this transaction was the one that corresponded to the liquidation.


```{r}

mutate_if(cdp[!is.na(TradePrice) & n != "exact"], is.numeric, function(x) {cell_spec(x=round(x,2))}) %>%
  kable(escape = FALSE, align = "r") %>%
  kable_styling(c("striped", "condensed"), full_width = FALSE)

```


Here is the rest of the CDP liquidation data (the exact matches):


```{r}

mutate_if(cdp[n == "exact"], is.numeric, function(x) {cell_spec(x=round(x,2))}) %>%
  kable(escape = FALSE, align = "r") %>%
  kable_styling(c("striped", "condensed"), full_width = FALSE)

```


Row
---

### Sources:

Last updated: `r Sys.time()`

* [Subscan.io](https://subscan.io)

* R source code [dashboard_liquidation.Rmd](https://github.com/AcalaNetwork/karura-reports)
