---
title: "Acala / Karura Staking Dashboards"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    social: menu
    source_code: embed
---

```{css custom1, echo=FALSE}
.dataTables_scrollBody {
    max-height: 100% !important;
}
```

```{r global, include=FALSE}
library(knitr)

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)


library(kableExtra)
library(formattable)
library(lubridate)
library(flexdashboard)
library(DT)
library(subscanr)
library(ghql)
x <- GraphqlClient$new()

# Helper function to concat
`%+%` <- function(a, b) paste0(a, b)

```

```{r tokens, cache = TRUE, include=FALSE}

endpage <- 2e9

KSM_tokens <- getAccountBalance_acala_token("karura", window = 1, filter = 'filter: {tokenId: {in: ["KSM","LKSM"]}, total: {greaterThan: "0"}} ', endpage = endpage)
KSM_token_wide <- dcast(KSM_tokens, accountId ~ tokenId, value.var = 'total')

DOT_tokens <- getAccountBalance_acala_token("acala", window = 1, filter = 'filter: {tokenId: {in: ["DOT","LDOT"]}, total: {greaterThan: "0"}} ', endpage = endpage)
DOT_token_wide <- dcast(DOT_tokens, accountId ~ tokenId, value.var = 'total')

```

```{r loans, cache = TRUE, include=FALSE}

aUSD_karura <- getAccountBalance_acala_token("karura", window = 1, filter = 'filter: {tokenId: {in: ["ACA","KUSD","AUSD"]}, total: {greaterThan: "0"}} ', endpage = endpage)
aUSD_karura_wide <- dcast(aUSD_karura, accountId ~ tokenId, value.var = 'total')


aUSD_acala <- getAccountBalance_acala_token("acala", window = 1, filter = 'filter: {tokenId: {in: ["ACA","KUSD","AUSD"]}, total: {greaterThan: "0"}} ', endpage = endpage)
aUSD_acala_wide <- dcast(aUSD_acala, accountId ~ tokenId, value.var = 'total')


loans_acala <- getPositions_acala_loan("acala", window = 1, filter = 'filter: {collateralId: {in: ["aUSD","kUSD","ACA","DOT","LDOT","KSM","LKSM"]}} ', endpage = endpage)
loans_acala_wide <- dcast(loans_acala, ownerId ~ collateralId, value.var = c('debitAmount','depositAmount'))


loans_karura <- getPositions_acala_loan("karura", window = 1, filter = 'filter: {collateralId: {in: ["aUSD","kUSD","ACA","DOT","LDOT","KSM","LKSM"]}} ', endpage = endpage)
loans_karura_wide <- dcast(loans_karura, ownerId ~ collateralId, value.var = c('debitAmount','depositAmount'))

```

```{r balances}

karura_addr <- merge(KSM_token_wide, aUSD_karura_wide, by = 'accountId', all = TRUE)
karura_addr <- merge(karura_addr, loans_karura_wide, by.x = 'accountId', by.y = 'ownerId', all = TRUE)


acala_addr <- merge(DOT_token_wide, aUSD_acala_wide, by = 'accountId', all.x = TRUE)
acala_addr <- merge(acala_addr, loans_acala_wide, by.x = 'accountId', by.y = 'ownerId', all = TRUE)

```

# Karura {.tabset}

Row
----

### KSM analysis based on `r karura_addr[, .N]` users

1) None = Default
2) KSM on Karura but no LKSM = Karura KSM Balance > 0
3) LKSM User = LKSM Balance > 0
4) LP User = depositAmount_LKSM > 0

```{r KSM}

# KSM
# KSM on Kusama only
# KSM on Karura but no LKSM
# LKSM user
# LP user
ksm_n <- karura_addr[, .N]
karura_addr[, KSM_Status := '1) None']
karura_addr[KSM > 0, KSM_Status := '2) KSM on Karura but no LKSM']
karura_addr[LKSM > 0, KSM_Status := '3) LKSM User']
karura_addr[depositAmount_LKSM > 0, KSM_Status := '4) LP User']
ksm_tbl <- karura_addr[, .N, by = 'KSM_Status'] %>%
  setorder(KSM_Status)
ksm_tbl2 <- karura_addr[, 100*round(.N / ksm_n, 3), by = 'KSM_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(KSM_Status)
ksm_tbl <- merge(ksm_tbl, ksm_tbl2)

knitr::kable(ksm_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```

Row
----

### AUSD (on Karura) analysis based on `r karura_addr[, .N]` users

1) None = Default
2) AUSD Vault Open = depositAmount_KSM > 0 OR depositAmount_LKSM > 0
3) Vault open but no AUSD minted = depositAmount_KSM > 0 OR depositAmount_LKSM > 0 AND (is.na(debitAmount_KSM) AND is.na(debitAmount_LKSM)

```{r KUSD}

# aUSD
# No aUSD
# aUSD holder
# aUSD vault open
# Vault open but no aUSD minted
ausd_karura_n <- karura_addr[, .N]
karura_addr[, AUSD_Status := '1) None']
karura_addr[AUSD > 0, AUSD_Status := '2) AUSD Holder']
karura_addr[depositAmount_KSM > 0 | depositAmount_LKSM > 0, AUSD_Status := '3) AUSD Vault Open']
karura_addr[depositAmount_KSM > 0 | depositAmount_LKSM > 0 & (is.na(debitAmount_KSM) & is.na(debitAmount_LKSM)), AUSD_Status := '4) Vault open but no AUSD minted']
ausd_tbl <- karura_addr[, .N, by = 'AUSD_Status'] %>%
  setorder(AUSD_Status)
ausd_tbl2 <- karura_addr[, 100*round(.N / ausd_karura_n, 3), by = 'AUSD_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(AUSD_Status)

ausd_tbl <- merge(ausd_tbl, ausd_tbl2)

knitr::kable(ausd_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```


# Acala {.tabset}

Row
----

### DOT analysis 

1) None = Default
2) DOT on Acala but no LDOT = Acala DOT Balance > 0
3) LDOT User = LDOT Balance > 0
4) LP User = depositAmount_LDOT > 0

```{r DOT}

# DOT
# DOT on Acala but not LDOT
# LDOT users
# LP user
dot_n <- acala_addr[, .N]
acala_addr[, DOT_Status := '1) None']
acala_addr[DOT > 0, DOT_Status := '2) DOT on Acala but no LDOT']
acala_addr[LDOT > 0, DOT_Status := '3) LDOT User']
acala_addr[depositAmount_LDOT > 0, DOT_Status := '4) LP User']
dot_tbl <- acala_addr[, .N, by = 'DOT_Status'] %>%
  setorder(DOT_Status)
dot_tbl2 <- acala_addr[, 100*round(.N / dot_n, 3), by = 'DOT_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(DOT_Status)

dot_tbl <- merge(dot_tbl, dot_tbl2)

knitr::kable(dot_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```

Row
----

### AUSD (on Acala) analysis 

1) None = Default
2) AUSD Holder = AUSD Balance > 0
3) AUSD Vault Open = depositAmount_KSM > 0 OR depositAmount_LKSM > 0
4) Vault open but no AUSD minted = depositAmount_KSM > 0 OR depositAmount_LKSM > 0 AND (is.na(debitAmount_KSM) AND is.na(debitAmount_LKSM)

```{r AUSD}

# aUSD
# No aUSD
# aUSD holder
# aUSD vault open
# Vault open but no aUSD minted

ausd_acala_n <- acala_addr[, .N]
acala_addr[, AUSD_Status := '1) None']
acala_addr[AUSD > 0, AUSD_Status := '2) AUSD Holder']
acala_addr[depositAmount_ACA > 0 | depositAmount_DOT > 0 | depositAmount_LDOT > 0, AUSD_Status := '3) AUSD Vault Open']
acala_addr[depositAmount_ACA > 0 | depositAmount_DOT > 0 | depositAmount_LDOT > 0 & (is.na(debitAmount_ACA) & is.na(debitAmount_DOT) & is.na(debitAmount_LDOT)), AUSD_Status := '4) Vault open but no AUSD minted']
ausd_tbl <- acala_addr[, .N, by = 'AUSD_Status'] %>%
  setorder(AUSD_Status)
ausd_tbl2 <- acala_addr[, 100*round(.N / ausd_acala_n, 3), by = 'AUSD_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(AUSD_Status)

ausd_tbl <- merge(ausd_tbl, ausd_tbl2)

knitr::kable(ausd_tbl, escape = FALSE, align = c("l",rep("r",3))) %>%
  kable_styling()

```

Row
----

### ACA analysis 

1) None = Default
2) ACA Staker = depositAmount_ACA > 0
3) No ACA Staking = ACA Balance > 0 
4) No ACA = is.na(ACA Balance)

```{r ACA}

# names(acala_addr)
# summary(acala_addr$debitAmount_ACA)
# summary(acala_addr$depositAmount_ACA)
# summary(loans_acala_wide$debitAmount_ACA)
# summary(loans_acala_wide$depositAmount_ACA)
# 
# tmp <- loans_acala_wide[, .(ownerId, debitAmount_ACA,depositAmount_ACA)]
# tmp <- merge(tmp, acala_addr[, .(accountId, ACA, ACA_Status)], by.x = "ownerId", by.y="accountId", all = TRUE)

                        
# ACA
# ACA staker
# No ACA staking
# No ACA
aca_n <- acala_addr[, .N]
acala_addr[, ACA_Status := '1) None']
acala_addr[depositAmount_ACA > 0, ACA_Status := '2) ACA Staker']
acala_addr[ACA > 0 && is.na(depositAmount_ACA), ACA_Status := '3) No ACA Staking']
acala_addr[is.na(ACA) | ACA == 0, ACA_Status := '4) No ACA']
aca_tbl <- acala_addr[, .N, by = 'ACA_Status'] %>%
  setorder(ACA_Status)
aca_tbl2 <- acala_addr[, 100*round(.N / aca_n, 3), by = 'ACA_Status'] %>%
  setnames("V1", "Percent (%)") %>%
  setorder(ACA_Status)

aca_tbl <- merge(aca_tbl, aca_tbl2)

knitr::kable(aca_tbl, escape = FALSE, align = c("l",rep("r",2)) ) %>%
  kable_styling()


```

# Methodologh {.tabset}

* The Subquery Network _Acala Tokens_ project was used to get balances on Acala for DOT, LDOT, ACA, and AUSD and the *Karura Tokens* project was used for Karura for KSM, LKSM, and AUSD.
  - https://explorer.subquery.network/subquery/AcalaNetwork/acala-tokens
  - https://explorer.subquery.network/subquery/AcalaNetwork/karura-tokens
  
* The Subquery Network *Acala Loans* project was used to get deposit and debit balances on Acala for DOT, LDOT, ACA, and AUSD and the *Karura Loans* project was used for Karura for KSM, LKSM, and AUSD.
  - https://explorer.subquery.network/subquery/AcalaNetwork/acala-loans
  - https://explorer.subquery.network/subquery/AcalaNetwork/karura-loan
  
* The methodology for each Token is summarized in that section.

* The Acala / Karura data is as of `r Sys.time()`. 

